---
title: "Negotiation results"
author: "Frederick Thielen, Brenda Leeneman, Marc Koopmanschap"
date: "`r Sys.Date()`"
output: slidy_presentation
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(here::here("calculations.R"))

library("tatooheen")
library("kableExtra")
library("tidyverse")

# filter_groups <- c("5 (Tutor: Frederick)")
# 
# filter_groups <- c("4 (Tutor: Brenda)")
#filter_groups <- c("6 (Tutor: Marc)")

res <- res %>%
  filter(wg %in% filter_groups #,
         #gr == "A"
         )
```

## Share your experience

One of each group, please share your experience:

- Was the negotiation-power between GOV and PHARMA balanced?
- Was it difficult to derive an agreement?
- What were the main points of discussion?
- How did you perceive time (pressure)?


## Results (1/6): Overspent budget

```{r res1, echo = FALSE, message=FALSE}
res %>% 
  filter(gov_balance < 0) %>% 
  group_by(wg, gr) %>% 
  summarise(n = n()) %>% 
  fkbl(caption = "Number of times budget was overspent by working group and group",
       col.names = c("Working group",
                     "Group",
                     "Number of times budget was overspent")) %>% 
  fkbl_style()
```

## Results (2/6): Crowding-out

```{r res2, echo = FALSE, message=FALSE}
res %>%
  filter(crowd_out < 0) %>%
  select(wg, gr, round, crowd_out) %>% 
  fkbl(caption = "Crowding-out by working group and group",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Number of QALYs lost")) %>% 
  fkbl_style()
```

## Results (3/6): Average prices

```{r res6, echo = FALSE, message=FALSE}
res %>%
  rowwise() %>% 
  mutate(wght_price = weighted.mean(c(p1, p2, p3), c(n1, n2, n3)),
         perc_from_list_p = wght_price / 150000,
         av_disc_give = (1-perc_from_list_p) * 100) %>% 
  select(wg, gr, round, wght_price, av_disc_give) %>% 
  fkbl(caption = "(Weighted) average prices",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Weighted average price",
                     "Average discount to list price (150,000 Euro)")) %>% 
  fkbl_style()
```



## Results (4/6): Untreated patients

```{r res3, echo = FALSE, message=FALSE}
res %>%
  filter(n_pat_notx > 0) %>%
  select(wg, gr, round, n_pat_notx) %>%
  fkbl(caption = "Number of patients without treatment per working group, group, and round",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Number of patients without treatment")) %>% 
  fkbl_style(scale = T)
```

## Results (5/6): Average price per patient

```{r res4, echo = FALSE, message=FALSE, warning=F}
res %>%
  mutate(ppp = budget_impact / n_pat_tx) %>%
  group_by(round) %>%
  summarise(mean = mean(ppp, na.rm = T),
            min = min(ppp, na.rm = T),
            max = max(ppp, na.rm = T),
            sd = sd(ppp, na.rm = T)) %>%
  fkbl(digi = 0,
    caption = "Average price per patient, per round, across groups and working groups",
       col.names = c("Round",
                     "Mean",
                     "Min",
                     "Max",
                     "Std. dev.")) %>% 
  fkbl_style(scale = TRUE)
```

## Results (6/6): Total points

```{r res5, echo = FALSE, message=FALSE, warning=F}
res %>%
  select(wg, gr, round, gov_total, man_total) %>%
  arrange(wg, gr, round) %>% 
  fkbl(digi = 1,
    caption = "Total points group and round",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Total points: GOV",
                     "Total points: PHARMA")) %>% 
  fkbl_style(scale = TRUE)
```


```{r}
# ggplot(data = dat_plot, aes(x = Points, y = Institution)) +
#   geom_boxplot() +
#   theme_bw() +
#   facet_grid(round ~ gr) +
#   ggtitle("Overall distribution of points by case")
```

