---
author: The HTA course team
format:
  revealjs:
    theme: white
    embed-resources: true
    logo: signature2.png
    css: logo.css
    smaller: true
    scrollable: true
    df-print: paged
editor: 
  markdown: 
    wrap: 72
editor_options: 
  chunk_output_type: console
---
## The HTA negotiation game: results {background-color="purple" background-opacity=0.6}

<br> <br> <br> <br>

### The HTA course team

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source(here::here("calculations.R"))

library("tatooheen")
library("kableExtra")
library("tidyverse")

```

## Share your experience

One of each group, please share your experience:

- Was the negotiaton-power between HCP and HTD balanced?
- Was it difficult to derive an agreement?
- What were the main points of discussion?
- How did you perceive time (pressure)?


## Results (1/5): Overspent budget

```{r res1, echo = FALSE, message=FALSE}
res %>% 
  filter(gov_balance < 0) %>% 
  group_by(wg, gr) %>% 
  summarise(n = n()) %>% 
  fkbl(caption = "Number of times budget was overspent by working group and group",
       col.names = c("Working group",
                     "Group",
                     "Number of times budget was overspent")) %>%
  collapse_rows(columns = 1:2, valign = "top") %>% 
  fkbl_style() 
```

## Results (2/5): Crowding-out

```{r res2, echo = FALSE, message=FALSE}
res %>%
  filter(crowd_out < 0) %>%
  select(wg, gr, round, crowd_out) %>% 
  fkbl(caption = "Crowding-out by working group and group",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Number of QALYs lost")) %>% 
  collapse_rows(columns = 1:2, valign = "top") %>% 
  fkbl_style()
```

## Results (3/5): Untreated patients

```{r res3, echo = FALSE, message=FALSE}
res %>%
  filter(n_pat_notx > 0) %>%
  select(wg, gr, round, n_pat_notx) %>%
  fkbl(caption = "Number of patients without treatment per working group, group, and round",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Number of patients without treatment")) %>% 
  collapse_rows(columns = 1:2, valign = "top") %>% 
  fkbl_style(scale = T)
```

## Results (4/5): Average price per patient

```{r res4, echo = FALSE, message=FALSE, warning=F}
res %>%
  mutate(ppp = budget_impact / n_pat_tx) %>%
  group_by(round) %>%
  summarise(mean = mean(ppp, na.rm = T),
            min = min(ppp, na.rm = T),
            max = max(ppp, na.rm = T),
            sd = sd(ppp, na.rm = T)) %>%
  fkbl(digi = 0,
    caption = "Average price per patient, per round, across groups and working groups",
       col.names = c("Round",
                     "Mean",
                     "Min",
                     "Max",
                     "Std. dev.")) %>% 
  collapse_rows(columns = 1:2, valign = "top") %>% 
  fkbl_style(scale = TRUE)
```

## Results (5/5): Total points

```{r res5, echo = FALSE, message=FALSE, warning=F}
res %>%
  select(wg, gr, round, gov_total, man_total) %>%
  arrange(wg, gr, round) %>% 
  fkbl(digi = 1,
    caption = "Total points group and round",
       col.names = c("Working group",
                     "Group",
                     "Round",
                     "Total points: HCP",
                     "Total points: HTD")) %>% 
  collapse_rows(columns = 1:2, valign = "top") %>% 
  fkbl_style(scale = TRUE)
```


```{r}
# ggplot(data = dat_plot, aes(x = Points, y = Institution)) +
#   geom_boxplot() +
#   theme_bw() +
#   facet_grid(round ~ gr) +
#   ggtitle("Overall distribution of points by case")
```

